\documentclass[11pt,letterpaper]{moderncv}
\usepackage[margin=1in]{geometry}
\moderncvstyle{banking}
\moderncvcolor{black}

\urlstyle{same} % Forces URLs to use same font, rather than a monospace font
\usepackage{changepage} % For indenting blocks of text


\usepackage[sorting=yd, style=authortitle, maxnames=99, backend=bibtex]{biblatex} % sort as below, maxnames avoids et al
\DeclareSortingTemplate{yd}{ % Reverse chronological order, and then whatever order as listed in the .bib file
	\sort{
		\field{presort}
	}
	\sort[final]{
		\field{sortkey}
	}
	\sort[direction=descending]{
		\field{sortyear}
		\field{year}
		\literal{9999}
	}
}
\addbibresource{CV_preprints.bib}
\nocite{*} % Cite everything in the bib files

\name{Justin}{Yirka} % Unused, since we make our own header

% TO Do:
% Copy old stuff
% Add date in footer
% Update research interests
% Add info on coding experience
% Add links
% Change "internships" to "research assistantships"
% And break out of "research" section

%=========================================================================================
%  BEGIN DOCUMENT
%=========================================================================================
\begin{document}

\begin{center}
	{\Large\textbf{Justin Yirka}}
	
	\textit{Curriculum Vitae}
	
	B.S. in Computer Science and B.S. in Mathematics
	
	Virginia Commonwealth University, Richmond, VA, USA
	\vspace{\baselineskip}
	
	\href{mailto:yirkajk@vcu.edu}{YirkaJk@vcu.edu}
	
	(703) 229-7956
	
	\url{www.linkedin.com/in/yirkajk}	
\end{center}


%%% Increase vertical spacing in remainder of document (default parskip in moderncv is 0em) %%%
\setlength{\parskip}{0.5em}
\setlength\bibitemsep{\parskip}


%=========================================================================================
%  SECTION: Research Interests
%=========================================================================================
\section{Research Interests}
Quantum computing, algorithms, complexity theory


%=========================================================================================
%  SECTION: Education
%=========================================================================================
\section{Education}
\cventry{(Dual degree program) 2018}{B.S. in Computer Science}{Virginia Commonwealth University (VCU)}{Richmond, VA}{\textit{GPA: 3.98 / 4.0}}{}
\vspace{-\baselineskip}\vspace{-\parskip}
\cventry{}{B.S. in Mathematical Sciences}{}{}{}
{	
	\begin{adjustwidth}{.25in}{}
		Concentration in Pure Math\hspace{2em}Specialization in Data Science \newline
		Minor in Physics \newline
		University Honors
	\end{adjustwidth}
}


%=========================================================================================
%  SECTION: Research
%=========================================================================================
\section{Research}
%==========  Experience  =======================================================
\subsection{Experience}
\cventry{Summer 2018}{Research Assistant}{Graph Theory Computational Discovery Lab, VCU}{}{}
{	
	\begin{adjustwidth}{.25in}{}
		Supervisor: Craig Larson, Ph.D. \newline
		Topic: Use of automated conjecturing software to find conditions for graph hamiltonicity.
	\end{adjustwidth}
}

\cventry{Summer 2017}{NSF REU Undergraduate Researcher}
{
	$\!$\begin{minipage}{0.8\textwidth}
		Joint Center for Quantum Information and Computer Science (QUCIS), \newline
		University of Maryland (UMD)	
	\end{minipage}
}
{}{}
{	
	\begin{adjustwidth}{.25in}{}
		Supervisor: Andrew Childs, Ph.D. \newline
		Topic: Quantum tomography. Pure-state tomography with Pauli observables. \newline
		Support: NSF Research Experience for Undergraduates (REU)  CAAR. PI: William Gasarch, Ph.D.
	\end{adjustwidth}
}

\cventry{2015--2016}{Undergraduate Research Assistant}{Quantum Computing Lab, VCU}{}{}
{	
	\begin{adjustwidth}{.25in}{}
		Supervisor: Sevag Gharibian, Ph.D. \newline
		Topics: Quantum computational complexity, complexity of local measurements, quantum oracle classes (e.g. $\textup{P}^{\textup{QMA}[\log]}$), quantum variants of the polynomial hierarchy.
	\end{adjustwidth}
}


%==========  Pre-prints  =======================================================
\printbibliography[heading=subbibliography, title={Pre-prints}, keyword=preprint]

%%==========  Conference presentations  =======================================================

%%==========  Public-audience talks  =======================================================


%==========  Journal publications  =======================================================

%==========  Invited talks  =======================================================

%==========  Expository writing  =======================================================

%=========================================================================================
%  SECTION: Scholarships
%=========================================================================================
\section{Scholarships \small{(all dollar amounts in USD)}} 
\cventry{2014--2018}{\$110,000}{Presidential Scholarship}{}{Virginia Commonwealth University}
{	
\begin{adjustwidth}{.25in}{}
	Top scholarship offered. Full cost of 4-year tuition, room, and board. \newline
	Awarded to 0.6\% of students
\end{adjustwidth}
}

\cventry{2014}{\$80,000}{Presidential Scholarship \textit{\textmd{[unable to accept]}}} {}{Worcester Polytechnic Institute}{}

\cventry{2014}{\$100,000}{Rensselaer Medal Merit Scholarship \textit{\textmd{[unable to accept]}}} {}{Rensselaer Polytechnic Institute}{}

%=========================================================================================
%  SECTION: Funding
%=========================================================================================
\section{Funding}
\cventry{2016--2018}{\$1,900}{Event grants for \textit{RamDev} seminar series}{}{VCU Student Government Association}{}

\cventry{2017}{\$500}{Travel grant for presentation at QIP 2017}{}{VCU Honors College}{}

\cventry{2016}{\$550}{Travel grant for presentation at NCUR 2016}{}{VCU Honors College}{}


%=========================================================================================
%  SECTION: Awards and Honors
%=========================================================================================
\section{Awards and Honors}
\cventry{2018}{VCU College of Humanities and Sciences}{Pure Mathematics Award}{}{}
{
	\begin{adjustwidth}{.25in}{}
		Awarded to student in pure mathematics concentration with highest graduating GPA.
	\end{adjustwidth}
}

\cventry{2017}{VCU School of Engineering}{Mark A. Sternheimer Capstone Design Award}{}{}
{
	\begin{adjustwidth}{.25in}{}
		For ``innovation and entrepreneurship'' of senior project developing mobile app. \newline
		Included grant of \$660.
	\end{adjustwidth}
}

\cventry{2015}{Virginia Commonwealth University}{University Student Scholar Award}{}{}{}

\cventry{2015}{VCU Symposium for Undergraduate Research and Creativity}{Launch Award for Outstanding Research Poster}{}{}
{
	\begin{adjustwidth}{.25in}{}
		For poster ``Evaluation of TCP header fields for data overhead efficiency''.
	\end{adjustwidth}
}

\cventry{2014}{Grade-school robotics program, Prince William County Schools, VA}{Volunteer of the Year}{}{}{}


%=========================================================================================
%  SECTION: Teaching Experience
%=========================================================================================
\section{Teaching Experience}
%==========  VCU  =======================================================
\subsection{VCU}
\cventry{(2 semesters) 2016--2017}{Algebra with Applications \small{(MATH 141)}}{Teaching Assistant}{}{}
{
	\begin{adjustwidth}{.25in}{}
		Assisted with in-class work, offered tutorials, graded assignments. \newline
		Average student evaluation scores --- Fall 2016: 4.78 / 5.0, Spring 2017: 4.36 / 5.0.
	\end{adjustwidth}
}

\cventry{Fall 2016}{Honors freshman mentorship program}{Mentor for 1\textsuperscript{st} year student}{}{}{}

\cventry{Fall 2015}{Honors Rhetoric \small{(HONR 200)} --- first-year honors writing and research course}{Teaching Assistant}{}{}
{
	\begin{adjustwidth}{.25in}{}
		Assisted with in-class work and critiqued student papers.
	\end{adjustwidth}
}

%==========  Other  =======================================================
\subsection{Other}
\cventry{2016--2018}{CPR, first-aid, and lifeguarding courses}{Instructor}{}{}{Department of Parks and Recreation, Prince William County, VA}

%=========================================================================================
%  SECTION: Service
%=========================================================================================
\section{Service}
%==========  University service (VCU)  =======================================================
\subsection{University service (VCU)}
\cventry{2016--2018}{Department of Computer Science}{Student Advisory Board member}{}{}
{
	\begin{adjustwidth}{.25in}{}
		\begin{itemize}%
			\item Invited to School of Engineering strategic planning retreat, 2017 (only CS undergraduate).
			\item Participated in hiring interviews for new faculty, 2017 (one of two students to participate).
		\end{itemize}
	\end{adjustwidth}
}

\cventry{(2 academic years) 2016--2017}{Honors College}{Senior Reader for Honors graduation dossiers}{}{}
{
	\begin{adjustwidth}{.25in}{}
		Assessed papers submitted in fulfillment of University Honors. Coordinated other readers.
	\end{adjustwidth}
}

\cventry{2017}{Department of Computer Science}{Panelist --- Career workshop for freshman mentorship program}{}{}{}

\cventry{2017}{Honors College}{Panelist --- Undergraduate conference preparation workshops}{}{}{}

\cventry{2016}{VCU Symposium for Undergraduate Research and Creativity}{Judge --- Launch Award for Outstanding Research Poster}{}{}{}

\cventry{2016}{Major League Hacking (MLH) and VCU Department of Computer Science}{Organizer --- Local Hack Day of Richmond, VA}{}{}
{
	\begin{adjustwidth}{.25in}{}
		Hosted event for 30 students including 12 high school students.
	\end{adjustwidth}
}

%==========  Extracurricular service  =======================================================
\subsection{Extracurricular service}
\cventry{2016--2018}{RamDev: Software Development at VCU}{Founder and President}{}{}
{
	\begin{adjustwidth}{.25in}{}
		\begin{itemize}
			\item Coordinated 46 weekly seminars including 9 corporate speakers.
			\item Secured and managed \$2400 in funding and resources.
			\item Increased weekly attendance to 20 students, becoming largest C.S. organization at VCU.
		\end{itemize}
	\end{adjustwidth}
}

%==========  Community involvement  =======================================================
\subsection{Community service}
\cventry{2011--2015}{Prince William County Schools, VA}{Volunteer for grade school \textup{FIRST \& Vex} robotics competitions}{}{}
{
	\begin{adjustwidth}{.25in}{}
		Awarded ``Volunteer of the Year'', 2014.
	\end{adjustwidth}
}

\cventry{2014}{Wilder Middle School, Richmond, VA}{Mentor to middle school \textup{Vex} robotics team}{}{}{}


\section{Master thesis}
\cvitem{title}{\emph{Title}}
\cvitem{supervisors}{Supervisors}
\cvitem{description}{Short thesis abstract}

\section{Experience}
\subsection{Vocational}
\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines.\newline{}%
	Detailed achievements:%
	\begin{itemize}%
		\item Achievement 1;
		\item Achievement 2, with sub-achievements:
		\begin{itemize}%
			\item Sub-achievement (a);
			\item Sub-achievement (b), with sub-sub-achievements (don't do this!);
			\begin{itemize}
				\item Sub-sub-achievement i;
				\item Sub-sub-achievement ii;
				\item Sub-sub-achievement iii;
			\end{itemize}
			\item Sub-achievement (c);
		\end{itemize}
		\item Achievement 3.
\end{itemize}}
\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}
\subsection{Miscellaneous}
\cventry{year--year}{Job title}{Employer}{City}{}{Description}

\section{Languages}
\cvitemwithcomment{Language 1}{Skill level}{Comment}
\cvitemwithcomment{Language 2}{Skill level}{Comment}
\cvitemwithcomment{Language 3}{Skill level}{Comment}

\section{Computer skills}
\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

\section{Interests}
\cvitem{hobby 1}{Description}
\cvitem{hobby 2}{Description}
\cvitem{hobby 3}{Description}

\section{Extra 1}
\cvlistitem{Item 1}
\cvlistitem{Item 2}
\cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}

\section{Extra 2}
\cvlistdoubleitem{Item 1}{Item 4}
\cvlistdoubleitem{Item 2}{Item 5}
\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}

\section{References}
\begin{cvcolumns}
	\cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
	\cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
	\cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
\end{cvcolumns}

\end{document}

